---
title: "STATS 250 Lab 9 Report"
author: "YOUR NAME GOES HERE IN QUOTES"
date: "TODAY'S DATE GOES HERE IN QUOTES"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
    css: assets/styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("plot_t.R") # This imports the plot_t() function
```

# Instructions

Welcome to Lab 9! Complete the following exercises designed to help you understand the simulation process for making inference about a population proportion. It is important that you keep your answers inside the ".answer" blocks. Do NOT delete the three colon blocks (:::) and keep your responses between them. Use the tutorial for help, and feel free to ask questions on Piazza or email your lab instructor.

Depending on your instruction method (synchronous or asynchronous), complete the following exercises collaboratively.

1. **Synchronous remote:** Work with your peers in breakout rooms during the synchronous lab.
1. **Asynchronous remote:** Use Piazza for asynchronous collaboration.

**Collaborators:** If applicable, replace this text with the names of anyone you collaborated with on this project.

**NOTE:** If you perform a calculation in R and assign it a name but do not print the value in your knitted document, we reserve the right to deduct points.

# Background

:::{.background}
"That standard of 98.6 degrees Fahrenheit was made famous by German physician Carl Reinhold August Wunderlich, who published the figure in a book in 1868. Modern studies, however, have called that number into question, suggesting that it’s too high. A recent study, for example, found the average temperature of 25,000 British patients to be 97.9 F. "^[https://med.stanford.edu/news/all-news/2020/01/human-body-temperature-has-decreased-in-united-states.html]

Is this still the case? Some A team at Stanford led by Julie Parsonnet, MD, recently compiled a dataset of over 500,000 body temperature measurements from adult patients who visited Stanford Health Care between 2007 and 2017 to examine this question. In this lab, we'll be looking at a subset of 1,000 of those measurements.^[Protsiv, Myroslava, et al. “Decreasing Human Body Temperature in the United States since the Industrial Revolution.” ELife, edited by Mark Jit et al., vol. 9, Jan. 2020, p. e49555. eLife, doi:10.7554/eLife.49555.]

Using the data in `body_temp.csv`, address the following research question:

> Is the mean human body temperature in the United States lower than 98.6 degrees Farenheit?

:::

## Question 1

:::{.question}
Read the data `body_temp.csv` into R. Provide numerical summaries AND one graphical summary of the `temp` variable.
:::

:::{.answer}
```{r question1, error = T}
# Replace this comment with code required for Question 1. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```
:::

## Question 2

:::{.question}
Write the appropriate hypotheses for addressing the research question *using symbols only*. 
:::

:::{.answer}
$H_0$: replace this text with your null hypothesis

$H_A$: replace this text with your alternative hypothesis
:::

## Question 3

:::{.question}
Define the parameter you used in Question 2.
:::

:::{.answer}
Replace this text with your answer to Question 3.
:::


## Question 4

:::{.question}
Check the two conditions needed to use the $t$ distribution to create confidence intervals or perform hypothesis tests for the `temp` variable.
:::

:::{.answer}
```{r question4, error = T}
# Replace this comment with code required for Question 4. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```

Replace this text with any necessary written answer for Question 4.

:::

## Question 5

:::{.question}
Use R as a calculator to compute the (estimated) standard error of $\bar{x}$ (the sample mean body temperature) and report the degrees of freedom of the $t$ distribution we'll use for constructing confidence intervals and performing hypothesis tests.
:::

:::{.answer}
```{r question5, error = T}
# Replace this comment with code required for Question 5. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```

Replace this text with any necessary written answer for Question 5.

:::

## Question 6

:::{.question}
Find the $t^*$ value needed to create a 98% confidence interval for this data. That is, using the degrees of freedom you found in Question 5, find the quantiles of the $t(df)$ distribution such that 98% of the data is between those two numbers. Include an appropriate visualization using `plot_t()`.
:::

:::{.answer}
```{r question6, error = T}
# Replace this comment with code required for Question 6. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```
:::

## Question 7

:::{.question}
Use your answers to Questions 1, 5, and 6 to construct a 98% confidence interval for the mean human body temperature in the United States, using R as a calculator. You should do this by using formulas, not `t.test()`.
:::

:::{.answer}
```{r question7, error = T}
# Replace this comment with code required for Question 5. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```

Replace this text with any necessary written answer for Question 7.

:::


## Question 8

:::{.question}
Use `t.test()` to test your hypotheses in Question 3.
:::

:::{.answer}
```{r question8, error = T}
# Replace this comment with code required for Question 8. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```
:::

## Question 9 

:::{.question}
Use `plot_t()` to create an appropriate visualization of the test statistic and p-value you found in Question 8.
:::

:::{.answer}
```{r question9, error = T}
# Replace this comment with code required for Question 9. (Remember that this text is a comment, so R ignores it; you can delete it if you want.) If you don't delete it, **start your code on a new line that doesn't start with #**

```
:::


## Wrap-Up and Submission

At the top of the document, make sure you've changed the `author` field to your name (in quotes!). If you'd like, change the date as well.

**When you've finished the lab, click the Knit button one last time.**


### Submission instructions
#### If you're using RStudio Cloud
1. In the Files pane, check the box next to `lab09-report.html`.
2. Click More > Export...
3. Click Download and save the file on your computer in a folder you'll remember and be able to find later. You can just call the file `lab09-report.html` or whatever else you'd like (as long as you remember what you called it).

#### If you're using RStudio installed on your computer
1. locate the `lab09-report.html` file on your computer. The file will be saved in the location indicated at the top of the files pane.

#### Submission to Canvas

1. Click the "Assignments" panel on the left side of the page. Scroll to find "Lab 9", and open the assignment. Click "Submit Assignment". 
2. Towards the bottom of the page, you'll be able to choose `lab09-report.html` from the folder you saved it in from RStudio Cloud or noted if you're using RStudio Desktop. **You will only be able to upload a .html file -- do not upload any other file type.**
  3. Click "Submit Assignment". You're done! 
